---
title: "Introduction to the thundeR package"
author: "Bartosz Czernecki, Mateusz Taszarek, Piotr Szuster"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the thundeR package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(scipen=999)
```

`**thundeR**` is a freeware R package and collection of functions for rapid computation and visualisation of convective parameters commonly used in the operational prediction of severe convective storms. Core algorithm is based on a highly optimized C++ code implemented into R language via RCPP. This solution allows to compute over 100 thermodynamic and kinematic parameters in less than 0.02s per profile and process large numerical datasets such as reanalyses or operational NWP models in a fairly low amount of time. This package was developed by research meteorologists specializing in severe convective storms and is constantly updated with new features. Its main purpose is to allow operational meteorologists and researchers a quick and easy evaluation of convective environments.



## Main functions:

- `**sounding_compute()**` - Function calculates presently over 100 atmospheric thermal-, kinematic- and composite indices (e.g. CAPE, CIN, Lapse Rates, EHI, STP, SCP, etc...) related mostly to severe weather phenomena (Thunderstorms, Large Hail, Tornadoes, etc...)
 
- `**sounding_plot()**` - Generate Skew-T, hodograph and summary of most important convective indices on a single plot
 
- `**sounding_save()**` - Auxiliary function to 'sounding_plot' that plots a composite \ of Skew-T, hodograph and other relavant rawindsonde-derived profiles \ on a single layout and saves it into graphical file. \ Useful if graphical window is too small.

- `**get_sounding()**` - Downloading measurements of the vertical profile of atmosphere (aka rawinsonde data) in a form convenient to use with `thunder` package


## Examples

Examples shows aplication of thunder

#### Example 1

Download exemplary sounding profile and create a composite layout:

```{r example1, eval = TRUE, fig.width = 9, fig.height = 6, fig.fullwidth = TRUE}
library(thunder)
pressure <- c(1000, 855, 700, 500, 300, 100, 10)
altitude <- c(0, 1500, 2500, 6000, 8500, 12000, 25000)
temp <- c(25, 10, 0, -15, -30, -50, -92)
dpt <- c(20, 5, -5, -30, -55, -80, -99)
wd <- c(0, 90, 135, 180, 270, 350, 0)
ws <- c(5, 10, 20, 30, 40, 5, 0)
sounding_plot(pressure, altitude, temp, dpt, wd, ws, 
              parcel = "MU", title = "Test thunder package")

```

### Example 2

compute severe weather related indices

```{r example2, eval = TRUE}
sounding_compute(pressure, altitude, temp, dpt, wd, ws)
```


## Details:

### 1. Parameters:

Below is the full list of parameters computed with the `sounding_compute()` function:

**Parcel parameters:**

[1] MU_CAPE – convective available potential energy, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are J/kg.

[2] MU_03km_CAPE – convective available potential energy between surface and 3 km AGL, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are J/kg.

[3] MU_HGL_CAPE – convective available potential energy in a hail growth layer (between 0°C and −20°C), derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are J/kg.

[4] MU_CIN – convective inhibition, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are J/kg.
 	
[5] MU_LCL_HGT – height of the lifted condensation level, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are m AGL. 

[6] MU_LFC_HGT – height of the level of free convection, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are m AGL. 

[7] MU_EL_HGT – height of the equilibrium level, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are m AGL. 

[8] MU_LI – lifted index, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are K.
 
[9] MU_WMAX – the maximum updraft speed in a thunderstorm (a square root of two times CAPE), derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are m/s. 
	
[10] MU_EL_TEMP – temperature of the equilibrium level, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are °C. 

[11] MU_LCL_TEMP – temperature of the lifted condensation level, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are °C.  

[12] MU_LFC_TEMP – temperature of the level of free convection, derived from the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are °C. 

[13] MU_MIXR – mixing ratio at the height of the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are g/kg.
 
[14] SB_CAPE – convective available potential energy, derived from the surface-based parcel. Units are J/kg.

[15] SB_03km_CAPE – convective available potential energy between surface and 3 km AGL, derived from the surface-based parcel. Units are J/kg.

[16] SB_HGL_CAPE – convective available potential energy in a hail growth layer (between 0°C and −20°C), derived from the surface-based parcel. Units are J/kg.

[17] SB_CIN – convective inhibition, derived from the surface-based parcel. Units are J/kg.
 	
[18] SB_LCL_HGT – height of the lifted condensation level, derived from the surface-based parcel. Units are m AGL. 

[19] SB_LFC_HGT – height of the level of free convection, derived from the surface-based parcel. Units are m AGL. 

[20] SB_EL_HGT – height of the equilibrium level, derived from the surface-based parcel. Units are m AGL. 

[21] SB_LI – lifted index, derived from the surface-based parcel. Units are K.
 
[22] SB_WMAX – the maximum updraft speed in a thunderstorm (a square root of two times CAPE), derived from the surface-based parcel. Units are m/s. 
	
[23] SB_EL_TEMP – temperature of the equilibrium level, derived from the surface-based parcel. Units are °C. 

[24] SB_LCL_TEMP – temperature of the lifted condensation level, derived from the surface-based parcel. Units are °C.  

[25] SB_LFC_TEMP – temperature of the level of free convection, derived from the surface-based parcel. Units are °C. 

[26] SB_MIXR – mixing ratio at the height of the surface-based parcel. Units are g/kg.

[27] ML_CAPE – convective available potential energy, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are J/kg.

[28] ML_03km_CAPE – convective available potential energy between surface and 3 km AGL, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are J/kg.

[29] ML_HGL_CAPE – convective available potential energy in a hail growth layer (between 0°C and −20°C), derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are J/kg.

[30] ML_CIN – convective inhibition, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are J/kg.
 	
[31] ML_LCL_HGT – height of the lifted condensation level, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are m AGL. 

[32] ML_LFC_HGT – height of the level of free convection, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are m AGL. 

[33] ML_EL_HGT – height of the equilibrium level, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are m AGL. 

[34] ML_LI – lifted index, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are K.
 
[35] ML_WMAX – the maximum updraft speed in a thunderstorm (a square root of two times CAPE), derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are m/s. 
	
[36] ML_EL_TEMP – temperature of the equilibrium level, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are °C. 

[37] ML_LCL_TEMP – temperature of the lifted condensation level, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are °C.  

[38] ML_LFC_TEMP – temperature of the level of free convection, derived from the mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). Units are °C. 

[39] ML_MIXR – mixing ratio at the height of the surface-based parcel. Units are g/kg.

**Temperature and moisture parameters:**

[40] LR_01km – temperature lapse rate between surface and 1 km AGL. Units are K/km.

[41] LR_03km – temperature lapse rate between surface and 3 km AGL. Units are K/km.

[42] LR_24km – temperature lapse rate between 2 and 4 km AGL. Units are K/km.

[43] LR_36km – temperature lapse rate between 3 and 6 km AGL. Units are K/km.

[44] LR_500700hPa – temperature lapse rate between 500 and 700 hPa (if below ground level, the lowest available level is considered). Units are K/km.

[45] LR_500800hPa – temperature lapse rate between 500 and 800 hPa (if below ground level, the lowest available level is considered). Units are K/km.

[46] FRZG_HGT – height of freezing level (0°C) as a first available level counting from the surface. Units are m AGL.

[47] FRZG_wetbulb_HGT – height of wet-bulb freezing level (0°C) as a first available level counting from the surface. Units are m AGL.

[48] HGT_max_thetae_03km – height of the most-unstable parcel (highest theta-e between surface and 3 km AGL). Units are m AGL.
 	
[49] HGT_min_thetae_04km – height of the lowest theta-e between surface and 4 km AGL. Units are m AGL.

[50] Delta_thetae – difference in theta-e between the mean in 3–5 km AGL layer and surface. Units are K.

[51] Delta_thetae_HGL – difference in theta-e between mean in a hail growth layer (between 0°C and −20°C) and surface. Units are K.

[52] DCAPE – downdraft convective available potential energy, initialized from 4 km AGL with a mean theta-e in 3–5 km AGL layer. Units are J/kg.

[53] Cold_Pool_Strength – difference between surface temperature and temperature of the downdraft (derived from DCAPE) at the surface. Units are K.

[54] Wind_Index – based on original formula from McCann (1994), doi: https://doi.org/10.1175/1520-0434(1994)009<0532:WNIFFM>2.0.CO;2. Units indicate estimated wind gust potential in knots. 

[55] PRCP_WATER – precipitable water (entire column). Units are mm.

[56] Moisture_Flux_02km – mean wind speed multiplied by mean mixing ratio in the layer between surface and 2 km AGL. Units are g/s/m2.
 
[57] RH_02km – mean relative humidity between surface and 2 km AGL layer. Units are %.

[58] RH_25km – mean relative humidity between 2 and 5 km AGL layer. Units are %.

[59] RH_HGL – mean relative humidity in a hail growth layer (between 0°C and −20°C). Units are %.

**Kinematic parameters:**

[60] BS_01km – bulk wind shear between surface and 1 km AGL. Units are m/s.

[61] BS_02km – bulk wind shear between surface and 2 km AGL. Units are m/s.

[62] BS_03km – bulk wind shear between surface and 3 km AGL. Units are m/s.

[63] BS_06km – bulk wind shear between surface and 6 km AGL. Units are m/s.

[64] BS_08km – bulk wind shear between surface and 8 km AGL. Units are m/s.

[65] BS_36km – bulk wind shear between 3 and 6 km AGL. Units are m/s. 	

[66] BS_18km – bulk wind shear between 1 and 8 km AGL. Units are m/s. 	

[67] BS_EFF_MU – effective shear based on most-unstable parcel (highest theta-e between surface and 3 km AGL). See Thompson et al. (2007), doi: https://doi.org/10.1175/WAF969.1 for further details. Units are m/s. 	

[68] BS_EFF_SB – effective shear based on surface-based parcel. See Thompson et al. (2007), doi: https://doi.org/10.1175/WAF969.1 for further details. Units are m/s. 	 	

[69] BS_EFF_ML – effective shear based on mixed-layer parcel (theta and mixing ratio averaged over 0–500m AGL layer and initialized from surface). See Thompson et al. (2007), doi: https://doi.org/10.1175/WAF969.1 for further details. Units are m/s. 		

[70] BS_SFC_to_HGL – bulk wind shear between surface and −10°C. Units are m/s.  	

[71] BS_MU_LFC_to_HGL – bulk wind shear between most-unstable level of free convection and −10°C. Units are m/s.    	

[72] BS_SB_LFC_to_HGL – bulk wind shear between surface-based level of free convection and −10°C. Units are m/s.    	 	

[73] BS_ML_LFC_to_HGL – bulk wind shear between mixed-layer level of free convection and −10°C. Units are m/s.    	 

[74] MW_01km – mean wind speed between surface and 1 km AGL layer. Units are m/s. 

[75] MW_02km – mean wind speed between surface and 2 km AGL layer. Units are m/s. 

[76] MW_06km – mean wind speed between surface and 6 km AGL layer. Units are m/s.  

[77] MW_13km – mean wind speed between 1 and 3 km AGL layer. Units are m/s.  

[78] SRH_100m_RM – storm-relative helicity between surface and 100m AGL for right-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m2/s2.  

[79] SRH_500m_RM – storm-relative helicity between surface and 500m AGL for right-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m2/s2.   

[80] SRH_1km_RM – storm-relative helicity between surface and 1 km AGL for right-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m2/s2.   	

[81] SRH_3km_RM – storm-relative helicity between surface and 3 km AGL for right-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m2/s2.   	

[81] SRH_100m_LM – storm-relative helicity between surface and 100m AGL for left-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m2/s2.   

[82] SRH_500m_LM – storm-relative helicity between surface and 500m AGL for left-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m2/s2.    

[83] SRH_1km_LM – storm-relative helicity between surface and 1 km AGL for left-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m2/s2.    	

[84] SRH_3km_LM – storm-relative helicity between surface and 3 km AGL for left-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m2/s2.    	

[85] Bunkers_RM_A – azimuth for right-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are °.   	
[86] Bunkers_RM_M – wind speed for right-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m/s. 

[87] Bunkers_LM_A  – azimuth for left-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are °.	

[88] Bunkers_LM_M – wind speed for left-moving supercell vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m/s.  	

[89] Bunkers_MW_A  – azimuth for mean storm motion vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are °.	

[90] Bunkers_MW_M – wind speed for mean storm motion vector. See Bunkers et al. (2002), doi: https://doi.org/10.1175/1520-0434(2000)015<0061:PSMUAN>2.0.CO;2 for further details. Units are m/s.  	

**Composite parameters:**

[91] K_Index 	– based on original formula from George (1960): "Weather Forecasting for Aeronautics" Academic Press, London, 1960, p. 673. Units are K.

[92] Showalter_Index – based on original formula from Showalter (1953), doi: https://doi.org/10.1175/1520-0477-34.6.250. Units are K.  

[93] TotalTotals_Index – based on original formula from Miller (1972): "Notes on analysis and severe-storm forecasting procedures of the Air Force Global Weather Central", AWS Tech. Rpt. 200(rev), Air Weather Service, Scott AFB, IL. Units are K.

[94] SWEAT_Index – based on original formula from Bidner (1970): "The Air Force Global Weather Central severe weather threat (SWEAT) index—A preliminary report". Air Weather Service Aerospace Sciences Review, AWS RP 105-2, No. 70-3, 2-5. Parameter is dimensionless.
	
[95] STP – based on the fixed layer formula currently used on the Storm Prediction Center mesoanalysis (https://www.spc.noaa.gov/exper/mesoanalysis/) as of 1 March 2021. Parameter is dimensionless. 	

[96] STP_new – based on original formula from Coffer et al. (2019), doi: https://doi.org/10.1175/WAF-D-19-0115.1. Parameter is dimensionless.	

[97] SCP – based on Thompson et al. (2007), "An update to the supercell composite and significant tornado parameters". Preprints, 22nd Conf. on Severe Local Storms, Hyannis, MA, Amer. Meteor. Soc. P (Vol. 8), but with effective SRH replaced with surface to 3 km AGL SRH and effective bulk wind shear replaced with surface to 6 km AGL bulk wind shear. Parameter is dimensionless.  	

[98] SCP_new – based on formula from Gropp and Davenport (2018), doi: https://doi.org/10.1175/WAF-D-17-0150.1, but with effective SRH replaced with surface to 3 km AGL SRH. Parameter is dimensionless.	 	

[99] SHIP – based on formula currently used on the Storm Prediction Center mesoanalysis (https://www.spc.noaa.gov/exper/mesoanalysis/) as of 1 March 2021. Parameter is dimensionless.  	

[100] DCP – based on formula currently used on the Storm Prediction Center mesoanalysis (https://www.spc.noaa.gov/exper/mesoanalysis/) as of 1 March 2021. Parameter is dimensionless.   	

[101] MU_WMAXSHEAR – most-unstable WMAX multiplied by surface to 6 km AGL bulk wind shear. See Taszarek et al. (2020), doi: https://doi.org/10.1175/JCLI-D-20-0346.1 for further details. Units are m2/s2. 	 	

[102] SB_WMAXSHEAR – surface-based WMAX multiplied by surface to 6 km AGL bulk wind shear. See Taszarek et al. (2020), doi: https://doi.org/10.1175/JCLI-D-20-0346.1 for further details. Units are m2/s2. 	 		

[103] ML_WMAXSHEAR – mixed-layer WMAX multiplied by surface to 6 km AGL bulk wind shear. See Taszarek et al. (2020), doi: https://doi.org/10.1175/JCLI-D-20-0346.1 for further details. Units are m2/s2. 	 	 	

[104] MU_EFF_WMAXSHEAR – most-unstable WMAX multiplied by most-unstable effective bulk wind shear. See Taszarek et al. (2020), doi: https://doi.org/10.1175/JCLI-D-20-0346.1 for further details. Units are m2/s2. 	 	 	

[105] SB_EFF_WMAXSHEAR – surface-based WMAX multiplied by surface-based effective bulk wind shear. See Taszarek et al. (2020), doi: https://doi.org/10.1175/JCLI-D-20-0346.1 for further details. Units are m2/s2. 	 	  	

[106] ML_EFF_WMAXSHEAR – mixed-layer WMAX multiplied by mixed-layer effective bulk wind shear. See Taszarek et al. (2020), doi: https://doi.org/10.1175/JCLI-D-20-0346.1 for further details. Units are m2/s2. 	 	  	

### 2. Accuracy tables for `sounding_compute()` 

The interpolation algorithm used in the `sounding_compute()` function for integrating positive or negative (i.e. CAPE/CIN) buoyancy area impacts accuracy and speed of the performed task. The valid options for the `accuracy` parameter are: 1 - fast implementation (default), 2 - medium accuracy, 3 - very accurate) with the following vertical layers to be used for computations:

`accuracy = 1` - High performance but low accuracy. Dedicated for extremely large dataset or operational predictions when output data needs to be quickly available. 60 vertical layers. Approx. 20 times faster than high accuracy (3) settings:

```{r accuracy1, echo = FALSE}
c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1600, 1800, 2000, 2200, 2400, 2600, 2800, 3000, 3200, 3400, 3600, 3800, 4000, 4200, 4400, 4600, 4800, 5000, 5200, 5400, 5600, 5800, 6000, 6500, 7000, 7500, 8000, 8500, 9000, 9500, 10000, 10500, 11000, 11500, 12000, 12500, 13000, 13500, 14000, 15000, 16000, 17000, 18000, 19000, 20000)
```

`accuracy = 2` - Compromise between performance and accuracy. Recommended for processing large numerical weather prediction datasets such as meteorological reanalysis. Approx. 10 times faster than high accuracy (3) settings:

```{r accuracy2, echo = FALSE}
c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250, 260, 270, 280, 290, 300, 310, 320, 330, 340, 350, 360, 370, 380, 390, 400, 410, 420, 430, 440, 450, 460, 470, 480, 490, 500, 510, 520, 530, 540, 550, 560, 570, 580, 590, 600, 610, 620, 630, 640, 650, 660, 670, 680, 690, 700, 710, 720, 730, 740, 750, 775, 800, 825, 850, 875, 900, 925, 950, 975, 1000, 1025, 1050, 1075, 1100, 1125, 1150, 1175, 1200, 1225, 1250, 1275, 1300, 1325, 1350, 1375, 1400, 1425, 1450, 1475, 1500, 1525, 1550, 1575, 1600, 1625, 1650, 1675, 1700, 1725, 1750, 1775, 1800, 1825, 1850, 1875, 1900, 1925, 1950, 1975, 2000, 2025, 2050, 2075, 2100, 2125, 2150, 2175, 2200, 2225, 2250, 2275, 2300, 2325, 2350, 2375, 2400, 2425, 2450, 2475, 2500, 2525, 2550, 2575, 2600, 2625, 2650, 2675, 2700, 2725, 2750, 2775, 2800, 2825, 2850, 2875, 2900, 2925, 2950, 2975, 3000, 3050, 3100, 3150, 3200, 3250, 3300, 3350, 3400, 3450, 3500, 3550, 3600, 3650, 3700, 3750, 3800, 3850, 3900, 3950, 4000, 4050, 4100, 4150, 4200, 4250, 4300, 4350, 4400, 4450, 4500, 4550, 4600, 4650, 4700, 4750, 4800, 4850, 4900, 4950, 5000, 5050, 5100, 5150, 5200, 5250, 5300, 5350, 5400, 5450, 5500, 5550, 5600, 5650, 5700, 5750, 5800, 5850, 5900, 5950, 6000, 6100, 6200, 6300, 6400, 6500, 6600, 6700, 6800, 6900, 7000, 7100, 7200, 7300, 7400, 7500, 7600, 7700, 7800, 7900, 8000, 8100, 8200, 8300, 8400, 8500, 8600, 8700, 8800, 8900, 9000, 9100, 9200, 9300, 9400, 9500, 9600, 9700, 9800, 9900, 10000, 10100, 10200, 10300, 10400, 10500, 10600, 10700, 10800, 10900, 11000, 11100, 11200, 11300, 11400, 11500, 11600, 11700, 11800, 11900, 12000, 12250, 12500, 12750, 13000, 13250, 13500, 13750, 14000, 14250, 14500, 14750, 15000, 15250, 15500, 15750, 16000, 16250, 16500, 16750, 17000, 17250, 17500, 17750, 18000, 18250, 18500, 18750, 19000, 19250, 19500, 19750, 20000)
```

`accuracy = 3`: High accuracy - low performance setting recommended for viewing individual profiles. Interpolation done with 5 m vertical resolution step (i.e.: `0, 5, 10, ... 20000` m AGL)

### Performance comparison:

```{r performace, echo=TRUE}
t1 = system.time(sounding_compute(pressure, altitude, temp, dpt, wd, ws, accuracy = 1))
t2 = system.time(sounding_compute(pressure, altitude, temp, dpt, wd, ws, accuracy = 2))
t3 = system.time(sounding_compute(pressure, altitude, temp, dpt, wd, ws, accuracy = 3))
print(t1)
print(t2)
print(t3)
```



