---
title: "Introduction to the thunder package"
author: "Bartosz Czernecki, Mateusz Taszarek, Piotr Szuster"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the thunder package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(scipen=999)
```

The goal of the  **thunder** R package is to calculate severe weather related set of algorithms that can be used for analyze and visualize atmospheric (pseudo-)soundings.

## Functions

- **sounding_compute()** - Description
 
- **sounding_plot()** - Generate Skew-T, hodograph and summary of most important convective indices on a single plot
 
- **sounding_save()** - Auxiliary function to 'sounding_plot' that plots a composite \ of Skew-T, hodograph and other relavant rawindsonde-derived profiles \ on a single layout and saves it into graphical file. \ Useful if graphical window is too small.

- **get_sounding()** - Downloading measurements of the vertical profile of atmosphere (aka rawinsonde data) in a form convenient to use with `thunder` package


## Examples

Examples shows aplication of thunder

#### Example 1

Download exemplary sounding profile and create a composite layout:

```{r example1, eval = TRUE, fig.width = 9, fig.height = 6, fig.fullwidth = TRUE}
library(thunder)
pressure <- c(1000, 855, 700, 500, 300, 100, 10)
altitude <- c(0, 1500, 2500, 6000, 8500, 12000, 25000)
temp <- c(25, 10, 0, -15, -30, -50, -92)
dpt <- c(20, 5, -5, -30, -55, -80, -99)
wd <- c(0, 90, 135, 180, 270, 350, 0)
ws <- c(5, 10, 20, 30, 40, 5, 0)
sounding_plot(pressure, altitude, temp, dpt, wd, ws, 
              parcel = "MU", title = "Test thunder package")

```

### Example 2

compute severe weather related indices

```{r example2, eval = TRUE}
sounding_compute(pressure, altitude, temp, dpt, wd, ws)
```


## Details:

### 1. Accuracy tables for `sounding_compute()` 

`accuracy = 1`:

| Right | Left | Default | Center |
|------:|:-----|---------|:------:|
|   12  |  12  |    12   |    12  |
|  123  |  123 |   123   |   123  |
|    1  |    1 |     1   |     1  |